### 2022-11-28 README.Rmd
Changed version of INLA dependency (testing->stable)
Had some issues fitting the model with the testing version

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  dev = "png",
  out.width = "80%"
)
```

>>>>

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  fig.width = 8,
  fig.height = 4,
  dev = "png",
  out.width = "90%"
)
```
